---
title: "KODAQS Team"
authors:
  - name: "David"
  - name: "Elnari"
  - name: "Erik"
  - name: "Josefine"
  - name: "Ladislav"
  - name: "Lukas"
  - name: "Soyeon"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-title: "Contents"
    embed-resources: true
    code-fold: true
    code-tools: true
    code-summary: "Show code"
    theme: cosmo
    fig-width: 10
    fig-height: 7
    fig-dpi: 300
    number-sections: true
execute:
  warning: false
  message: false
  echo: true
editor: 
  markdown: 
    wrap: 72
---

# Preface

This Quarto document serves as the ***KODAQS Team***'s submission & presentation for the [DataFest Germany 2026](https://www.uni-mannheim.de/datascience/events/datafest-2026/), based on a [GitHub repository](https://github.com/simondavi/datafest_kodaqsteams/).

The document compiles various analyses done by the team, focussing on different aspects of data quality, namely:
1. a
2. language embeddings
3. 

```{mermaid}
flowchart LR
  A[Setup] --> B[Embeddings]
  B --> C{Bot Analyses}
  C --> D[Result one]
  C --> E[Result two]
  D --> F{Takeaways}
  E --> F{Takeaways}
```


# Setup

First, the script ensures interoperability & reproducibility, by:

```{mermaid}
flowchart LR
  A[setting the work directory] --> B[managing R packages]
  B -.-> C[creating 'output' directory]
```

```{r 00_setup}
#| label: 00_setup

options(repos = c(CRAN = "https://cran.r-project.org"))
set.seed(2026)

if (!require("here", quietly = TRUE)) install.packages("here")
library(here)
here::i_am("kodaqs_team_quarto.qmd")

if (!require("pacman", quietly = TRUE)) install.packages("pacman")
library(pacman)

pacman::p_load(
  tidyverse, jsonlite, glmnet, purrr, lubridate, sessioninfo
  )

# Output directory
output_dir <- here("output")
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)
```


# Cross-Language Embedding Audit

```{r 01_cross-lang}
#| label: 01_cross-lang
#| file: src/01_cross-lang.R
```

```{r 02_cross-lang-prep}
#| label: 02_cross-lang-prep
#| file: src/02_cross-lang-prep.R
```

```{py 03_cross-lang-reg}
#| label: 03_cross-lang-reg
#| file: src/03_cross-lang-reg.py
```


# Bot Analyses

```{r 04_bot-analysis}
#| label: 04_bot-analysis
#| file: src/04_bot-analysis.R
```


## Bot Prediction Using sap-rpt-1-oss

```{r 05_bot-pred-prep}
#| label: 05_bot-pred-prep
#| file: src/05_bot-pred-prep.R
```


```{py 06_bot-pred-analysis}
#| label: 06_bot-pred-analysis
#| file: src/06_bot-pred-analysis.py
```


## Malicious Bots

Wikipedia allows automated programs, known as *bots*, to perform repetitive maintenance tasks such as correcting links or updating formatting across many pages. These bots are typically approved by the Wikipedia community and are designed to operate transparently and reliably.

This section compares the official Wikipedia bot label with a custom metric detecting suspicious editing behaviour in the Swedish Wikipedia sample (*svwiki.json*).

The goal is to examine, whether the official bot label primarily captures well-behaved automated editors, while the proposed `malicious_bot_like` metric highlights potentially problematic editing patterns among human contributors.

```{r 07_mal-bot}
#| label: 07_mal-bot
#| file: src/07_mal-bot.R
```

### Key Insights

- The Wikipedia bot label mostly captures **\"good bots\"**, which show:
  - low revert rates
  - low edits per editor/page.

- The `malicious_bot_like` flag identifies **suspicious editors among humans**, who tend to have:
  - higher revert rates
  - slightly more concentrated editing activity.

- This suggests the metric highlights **potentially problematic users that are not flagged as bots**.

# Additional Information

This project is part of the [KODAQS Data Quality Academy Certificate Program](https://www.gesis.org/en/gesis-training/kodaqs-academy/kodaqs-data-quality-academy-certificate-program).

```{r 10_session_info}
#| label: 10_session_info

sessioninfo::session_info(pkgs = "attached", include_base = TRUE)
```

**Repository structure:**
```
repository/
├── kodaqs_team_quarto.qmd            # this file (main analysis script)
├── data/                             # raw data provided by the DataFest (not shared)
│   ├── arwiki.json                   # information about all edits to arabic articles
│   ├── dewiki.json                   # information about all edits to german articles
│   ├── enwiki.json                   # information about all edits to english articles
│   ├── eswiki.json                   # information about all edits to spanish articles
│   ├── frwiki.json                   # information about all edits to french articles
│   ├── itwiki.json                   # information about all edits to italian articles
│   ├── nlwiki.json                   # information about all edits to dutch articles
│   ├── page_info.json                # page-level information (154k observations)
│   ├── page_views.json               # page view information (36M observations)
│   ├── plwiki.json                   # information about all edits to polish articles
│   ├── ruwiki.json                   # information about all edits to russian articles
│   └── svwiki.json                   # information about all edits to swedish articles
├── extra/                            # additional resources provided by the DataFest
│   ├── access_json.R                 # 
│   ├── datafest_2026.ipynb           # 
│   └── resources_information.txt     # general information on the provided data
├── output/                           # generated tables and plots
├── src/                              # individual code chunks
│   ├── 01_cross-lang.R               # 
│   ├── 02_cross-lang-prep.R          # 
│   ├── 03_cross-lang-reg.py          # 
│   ├── 04_bot-analysis.R             # 
│   ├── 05_bot-pred-prep.R            # 
│   ├── 06_bot-prep-analysis.py       # 
│   └── 07_mal-bot.R                  # 
├── .gitignore                        #
├── LICENSE                           #
└── README.md                         #
```
