---
title: "KODAQS Team"
authors:
  - name: "David"
  - name: "Elnari"
  - name: "Erik"
  - name: "Josefine"
  - name: "Ladislav"
  - name: "Lukas"
  - name: "Soyeon"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-title: "Contents"
    embed-resources: true
    code-fold: true
    code-tools: true
    code-summary: "Show code"
    theme: cosmo
    fig-width: 10
    fig-height: 7
    fig-dpi: 300
    number-sections: true
execute:
  warning: false
  message: false
  echo: true
editor: 
  markdown: 
    wrap: 72
---

# Preface

This Quarto document serves as the ***KODAQS Team****'s* submission for the [DataFest Germany 2026](https://www.uni-mannheim.de/datascience/events/datafest-2026/), based on a public [GitHub repository](https://github.com/simondavi/datafest_kodaqsteams/).

The document compiles various analyses done by the team, focussing on different aspects of data quality, namely:

1. a
2. language embeddings
3. 

# Key Insights

Our collective insights pertain to conceptualisation disrepancies across Wikipedia language families. The key data quality issues we have identified in this regard include: conceptual ambiguity, contextual dependence/bias and a lack in standardization. We show this by first looking at the QID identifier variable, using examples of differences in terms of conceptualisation across languages, followed by looking at whether bots can be predicted in the same way in different language families.

```{mermaid}
flowchart LR
  A(Setup) --> B{QID as identifier?}
  B --> C[embeddings]
  B --> D[how pages differ]
  C --> E{Is bot?}
  D --> E{Is bot?}
  E --> F[a]
  E --> G[b]
  F --> H(Takeaways)
  G --> H(Takeaways)
```



# Setup

First, the script ensures interoperability & reproducibility, by:

```{mermaid}
flowchart LR
  A[setting the work directory] --> B[managing R packages]
  B -.-> C[creating the 'output' directory]
```

::: {.callout-warning}
The data for this project was provided by the DataFest and is not available directly in the repository. However, the data is publicly available via [Wikimedia](https://meta.wikimedia.org/wiki/Datasets). Since this document requires the data in order to run the code chunks and render the final html, **make sure that all required datasets are available in the *data/* folder**.
:::

```{r 00_setup}
#| label: 00_setup

options(repos = c(CRAN = "https://cran.r-project.org"))
set.seed(2026)

if (!require("here", quietly = TRUE)) install.packages("here")
library(here)
here::i_am("kodaqs_team_quarto.qmd")

if (!require("pacman", quietly = TRUE)) install.packages("pacman")
library(pacman)

pacman::p_load(
  tidyverse, jsonlite, glmnet, purrr, lubridate, knitr, sessioninfo
  )

# Output directory
output_dir <- here("output")
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)
```


# Cross-Language Embedding Audit

```{r 01_cross-lang}
#| label: 01_cross-lang
#| file: src/01_cross-lang.R
```

```{r 02_cross-lang-prep}
#| label: 02_cross-lang-prep
#| file: src/02_cross-lang-prep.R
```

```{py 03_cross-lang-reg}
#| label: 03_cross-lang-reg
#| file: src/03_cross-lang-reg.py
```


# Bot Analyses

```{r 04_bot-analysis}
#| label: 04_bot-analysis
#| file: src/04_bot-analysis.R
```


## Bot Prediction Using sap-rpt-1-oss

```{r 05_bot-pred-prep}
#| label: 05_bot-pred-prep
#| file: src/05_bot-pred-prep.R
```


```{py 06_bot-pred-analysis}
#| label: 06_bot-pred-analysis
#| file: src/06_bot-pred-analysis.py
```


## Malicious Bots

Wikipedia allows automated programs, known as *bots*, to perform repetitive maintenance tasks such as correcting links or updating formatting across many pages. These bots are typically approved by the Wikipedia community and are designed to operate transparently and reliably.

This section compares the official Wikipedia bot label with a custom metric detecting suspicious editing behaviour in the Swedish Wikipedia sample (*svwiki.json*).

The goal is to examine, whether the official bot label primarily captures well-behaved automated editors, while the proposed `malicious_bot_like` metric highlights potentially problematic editing patterns among human contributors.

```{r 07_mal-bot}
#| label: 07_mal-bot
#| file: src/07_mal-bot.R
```

### Key Insights

- The Wikipedia bot label mostly captures **\"good bots\"**, which show:
  - low revert rates
  - low edits per editor/page.

- The `malicious_bot_like` flag identifies **suspicious editors among humans**, who tend to have:
  - higher revert rates
  - slightly more concentrated editing activity.

- This suggests the metric highlights **potentially problematic users that are not flagged as bots**.

# Additional Information

::: {.callout-note}
This project is part of the [KODAQS Data Quality Academy Certificate Program](https://www.gesis.org/en/gesis-training/kodaqs-academy/kodaqs-data-quality-academy-certificate-program).
:::

```{r 10_session_info}
#| label: 10_session_info

sessioninfo::session_info(pkgs = "attached", include_base = TRUE)
```
