---
title: "KODAQS Team"
authors:
  - name: "David"
  - name: "Elnari"
  - name: "Erik"
  - name: "Josefine"
  - name: "Ladislav"
  - name: "Lukas"
  - name: "Soyeon"
format:
  html:
    toc: true
    toc-location: left
    toc-depth: 3
    toc-title: "Contents"
    embed-resources: true
    code-fold: true
    code-tools: true
    code-summary: "Show code"
    theme: cosmo
    fig-width: 10
    fig-height: 7
    fig-dpi: 300
    number-sections: true
execute:
  warning: false
  message: false
  echo: true
editor: 
  markdown: 
    wrap: 72
---

# Preface

This Quarto document serves as the ***KODAQS Team***'s submission & presentation for the [DataFest Germany 2026](https://www.uni-mannheim.de/datascience/events/datafest-2026/), based on a [GitHub repository](https://github.com/simondavi/datafest_kodaqsteams/).

The document compiles various analyses done by the team, focussing on different aspects of data quality, namely:
1. a
2. language embeddings
3. 

```{mermaid}
flowchart LR
  A[Setup] --> B[Embeddings]
  B --> C{Bot Analyses}
  C --> D[Result one]
  C --> E[Result two]
  D --> F{Takeaways}
  E --> F{Takeaways}
```


# Setup

First, we need to make sure that the work is reproducible across devices:

```{mermaid}
flowchart LR
  A[set work directory] --> B[manage R packages]
  B -.-> C[create 'output' directory]
```

```{r 00_setup}
#| label: 00_setup

options(repos = c(CRAN = "https://cran.r-project.org"))
set.seed(2026)

if (!require("here", quietly = TRUE)) install.packages("here")
library(here)
here::i_am("kodaqs_team_quarto.qmd")

if (!require("pacman", quietly = TRUE)) install.packages("pacman")
library(pacman)

pacman::p_load(
  tidyverse, jsonlite, glmnet, purrr, lubridate, sessioninfo
  )

# Output directory
output_dir <- here("output")
if (!dir.exists(output_dir)) dir.create(output_dir, recursive = TRUE)
```


# Cross-Language Embedding Audit

```{r 01_cross-lang}
#| label: 01_cross-lang
#| file: src/01_cross-lang.R
```

```{r 02_cross-lang-prep}
#| label: 02_cross-lang-prep
#| file: src/02_cross-lang-prep.R
```

```{py 03_cross-lang-reg}
#| label: 03_cross-lang-reg
#| file: src/03_cross-lang-reg.py
```


# Bot Analyses

```{r 04_bot-analysis}
#| label: 04_bot-analysis
#| file: src/04_bot-analysis.R
```


## Bot Prediction Using sap-rpt-1-oss

```{r 05_bot-pred-prep}
#| label: 05_bot-pred-prep
#| file: src/05_bot-pred-prep.R
```


```{py 06_bot-pred-analysis}
#| label: 06_bot-pred-analysis
#| file: src/06_bot-pred-analysis.py
```


## Malicious Bots

```{r 07_mal-bot}
#| label: 07_mal-bot
#| file: src/07_mal-bot.R
```


# Additional Information



```{r 10_session_info}
#| label: 10_session_info

sessioninfo::session_info(pkgs = "attached", include_base = TRUE)
```

**Repository structure:**
```
repository/
├── kodaqs_team_quarto.qmd            # this file (main analysis script)
├── data/                             # raw data provided by the DataFest (not shared)
│   ├── arwiki.json                   # information about all edits to arabic articles
│   ├── dewiki.json                   # information about all edits to german articles
│   ├── enwiki.json                   # information about all edits to english articles
│   ├── eswiki.json                   # information about all edits to spanish articles
│   ├── frwiki.json                   # information about all edits to french articles
│   ├── itwiki.json                   # information about all edits to italian articles
│   ├── nlwiki.json                   # information about all edits to dutch articles
│   ├── page_info.json                # page-level information (154k observations)
│   ├── page_views.json               # page view information (36M observations)
│   ├── plwiki.json                   # information about all edits to polish articles
│   ├── ruwiki.json                   # information about all edits to russian articles
│   └── svwiki.json                   # information about all edits to swedish articles
├── extra/                            # additional resources provided by the DataFest
│   ├── access_json.R                 # 
│   ├── datafest_2026.ipynb           # 
│   └── resources_information.txt     # general information on the provided data
├── output/                           # generated tables and plots
├── src/                              # individual code chunks
│   ├── 01_cross-lang.R               # 
│   ├── 02_cross-lang-prep.R          # 
│   ├── 03_cross-lang-reg.py          # 
│   ├── 04_bot-analysis.R             # 
│   ├── 05_bot-pred-prep.R            # 
│   ├── 06_bot-prep-analysis.py       # 
│   └── 07_mal-bot.R                  # 
├── .gitignore                        #
├── LICENSE                           #
└── README.md                         #
```
